Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-06-13 longSC.tex
minor fix

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics. With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}. In {MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}. The detailed quantitative comparisons of the measured $v_n$ to the model calculations are provided in Appendix~\ref{sec:vn}.

>>>>

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics. With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}. In {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}. The detailed quantitative comparisons of the measured $v_n$ to the model calculations are provided in Appendix~\ref{sec:vn}.
